R Tools for Obspack, Footprints and Receptors (rtorf)

### 2024-03-18 README.Rmd
order index
readme

![GitHub commit
activity](https://img.shields.io/github/commit-activity/y/ibarraespinosa/rtorf)

@@

[![R-CMD-check](https://github.com/ibarraespinosa/torf/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ibarraespinosa/torf/actions/workflows/R-CMD-check.yaml)

@@

```{r, eval = F}
remotes::install_github("ibarraespinosa/rtorf")
```

@@

```{r}

@@

@@

## Recommendation for other applications
The approach to generate receptors depends on each type of 
observation and other considerations. For instance, aircraft with 
continuous observations at each second can be filtered and averaged 
every 20 seconds. In that way, the footprints are still 
representative and it would not be necessary to run HYSPLIT 
every second. Of course, it depends on the application 
and objective of the study. For this manuscript, we are 
presenting the generation of receptors based on tower observations.

>>>>

![GitHub commit
activity](https://img.shields.io/github/commit-activity/y/noaa-gml/rtorf)

@@

[![R-CMD-check](https://github.com/noaa-gml/torf/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/noaa-gml/torf/actions/workflows/R-CMD-check.yaml)

@@

```{r, eval = F}
remotes::install_github("noaa-gml/rtorf")
```

@@

## This exampel reads text files but it will be updated to read NetCDF

@@

```{r, eval = T, include = F}

categories <- c(
  "aircraft-pfp",
  "aircraft-insitu",
  "surface-insitu",
  "aircore",
  "surface-pfp",
  "tower-insitu",
  "shipboard-insitu",
  "flask"
)
obs <- "Z:/torf/obspack_ch4_1_GLOBALVIEWplus_v5.1_2023-03-08/data/txt/"
index <- obs_summary(obs = obs, verbose = T)

@@
